Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-05-08 paper/response.tex

Thank you for the positive assessment.
\end{item}

\begin{item} \label{newmetrics}
\textbf{With the current form of the results it is hard to compare the
improvements in terms of accuracy gained. This can be overcome by
including results such as physical distance between predicted paths and
ground truth observations. Such matrices are provided in the baseline
models \cite{Kitani2012} \cite{Karasev2016} \cite{Robicquet2016} with accuracy values in meters. }

Thank you for the suggestion. 
The objective of this paper was to develop a predictor that would be effective for use in the autonomous vehicle context. 
In this instance, to ensure safety it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
Since the ROC curve plots the true positive rate (i.e. the proportion of the ground truth trajectory that is correctly identified) against the false positive rate (i.e. the proportion of the generated set that does not correspond to the ground truth trajectory), it evaluates this aforementioned safety criteria for autonomous vehicles exactly.

On the other hand the Modified Hausdorff Distance (MHD) from \cite{Dubuisson1994} measures the average geometric distance between the ground-truth observed trajectory and the generated set of predictions. 
Though popular in evaluating the geometric proximity of the ground truth trajectory and a predicted set, it is not the best way to evaluate the utility of an algorithm in the autonomous vehicle context. 
Specifically consider the instance of a generated set of predictions which does not contain the ground-truth observed trajectory, but is close to the ground-truth trajectory geometrically. 
If this generated set of predictions was used in the autonomous vehicle context, it would not preclude certain portions of the space which the person occupied. 
Notice that in this instance the true positive rate would be zero meaning that the generated set of predictions was not useful.
Whereas the MHD would describe this generated set of predictions as informative.

Nevertheless, we addressed this concern by adding a comparison to the MHD which is summarized in the Figure \ref{MHD} below and included in the resubmitted version of our manuscript. 
Our approach outperforms the methods proposed in \cite{Kitani2012} and \cite{Alahi2016} in the intermediate term. 
At short times, the method described in \cite{Alahi2016} puts more weight on the direction of the observed trajectory which results in a narrow distribution that is closer to the trajectory. 
If you look at Figures \ref{bookstore} and \ref{death}, one can observe that the predictions generated using the method in \cite{Alahi2016} is geometrically closer to the observed trajectory but does not contain it which makes it less appropriate in the autonomous vehicle context.
At large scales,  the approached described in\cite{Kitani2012} outperforms all  others since it is given the endpoint of the trajectory. 
%\Ram{it would be useful if we summarized what we were seeing the MHD plot here. Meaning it would be helpful if you could say something to the effect that with respect to MHD we are good in the medium term. In addition it would be nice if we could see some sample trajectories from lstm to really illustrate that they aren't including the ground truth trajectory but are just close geometrically which contributes to their low MHD score. That image should be included in the resubmitted text and in this response letter}
We have included the following passage to explain both metrics in the revised submission:

\reversemarginpar\marginnote{\#4.5}
\response{ In our analysis, we sought a metric that evaluated the utility of prediction algorithms in the autonomous vehicle context. 
In this instance, it is critical that the generated set of predictions contains the ground-truth observed trajectory while including as few false positive detections as possible.
ROC curves which plot the true positive rate (i.e. the proportion of the ground truth trajectory that is correctly identified) against the false positive rate (i.e. the proportion of the generated set that does not correspond to the ground truth trajectory), evaluate this aforementioned safety criteria for autonomous vehicles exactly. 
The Area Under the Curve (AUC) is a standard measure of the quality of a predictor.  
The closer that this AUC is to one, the better the prediction algorithm.
Figure \ref{AUC} shows the analysis of the AUC of each algorithm versus time.

In addition, we evaluated the Modified Hausdorff Distance (MHD) from the ground truth trajectory to a sample from the predictions at each time to provide a geometric measure of how accurate the predictions are. 
Figure \ref{MHD} shows MHD plotted against time.
Though popular in evaluating the geometric proximity of the ground truth trajectory and a predicted set, it is not the most appropriate way to evaluate the utility of an algorithm in the autonomous vehicle context. 
Specifically consider the instance of a generated set of predictions which does not contain the ground-truth observed trajectory but is close to the ground-truth trajectory geometrically. 
If this generated set of predictions was used in the autonomous vehicle context, it would not preclude certain portions of the space which the person occupied. 
Notice that in this instance the true positive rate would be zero meaning that the generated set of predictions was not useful.
Whereas the MHD would describe this generated set of predictions as informative.
}

@@

\end{item}
\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{figures/mhd_results.eps}
	\caption{A comparison of the Modified Hausdorff Distance from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. At longer timescales the MHD to the trajectory of most algorithms converges. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms which assume that the end point of the trajectory is unknown.}
   \reversemarginpar\marginnote{\#4.10}
	\label{MHD}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{figures/the_results.eps}
	\caption{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the S-LSTM \cite{Alahi2016} model $100$ times to organically extract a less concentrated probability distribution from their algorithm, but their confidence combined with the over-reliance on social forces at moderate-to-large timescales lowered their performance.}
	\reversemarginpar\marginnote{\#4.9}
	\label{AUC}
\end{figure}

@@

\section*{Reviewer 2}
\begin{enumerate}
\begin{item}
\textbf{Keep the good work going. Interesting approach.}
\end{item}

Thank you for the kind comments.

\begin{item}
\textbf{
Need to be clearer and
dive a little bit deeper into the technical approach. }

Thank you for this criticism. 
We strengthened the description of our method for learning the motion model and quantifying the way that we tested our data as is described in our responses to the suggestions by other reviewers.

@@

\end{item}

\begin{item}
\textbf{
Need to use and apply more deep learning approaches such as social LSTM
or other machine methods.}

Thank you for the suggestion. 
We hope that we have addressed this criticism by including a review of literature of social motivated models, including S-LSTM, as well as a section on how social factors can be integrated into our model. 
In addition, we compared our approach against S-LSTM in addition to the method proposed in \cite{Kitani2012}. 
We included the visualizations in Figures \ref{bookstore} and \ref{death}, which are also included in our resubmission.

@@

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Kitani et al.}  }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/kit_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{S-LSTM} }  
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/lstm_1_2_t=100.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/lstm_1_2_t=300.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/lstm_1_2_t=360.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }  
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=50.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=130.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/bookstore/rand_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.2cm}
	\hspace{.5cm}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 1.66s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 4.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 12.33s$
	\end{minipage}	
	\caption{
		An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} suffer from the inability of their motion model to adequately match the speed of the agent. The algorithm in \cite{Alahi2016} is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}
	\label{bookstore}
\end{figure}

@@

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{S-LSTM}} 
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/lstm_1_2_t=100.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/lstm_1_2_t=300.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/lstm_1_2_t=380.jpg}
	\end{minipage}

	\vspace{0.1cm}
	\begin{minipage}[c]{0.5cm}
		\rotatebox{90}{\small{Random Walk} }
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=70.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=250.jpg}
	\end{minipage}
	\begin{minipage}[c]{0.3\linewidth}
		\includegraphics[width=\linewidth]{./figures/comparison/rand_death_1_2_t=370.jpg}
	\end{minipage}

	\vspace{0.2cm}
	\hspace{.5cm}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 2.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 8.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 12.33s$
	\end{minipage}

	\caption{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle. The algorithm in \cite{Alahi2016} is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}
	\label{death}
\end{figure}

### 2017-05-08 paper/pedestrian_forecasting_iros_2017.tex
fixed numbering in response letter and got the size of the text under 9 pages

%  For math environment 
\usepackage{amsmath,amssymb}
%\usepackage[linesnumbered]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{marginnote}
%\usepackage{algorithm2e}
\usepackage{caption}
%  For todo notes
\usepackage{todonotes}
%  For drawing Bayesian networks
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{tikz-cd}
\usepackage[justification=justified,font=footnotesize]{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{array}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{comment}
\usepackage{color}  % For Highlighting

@@

%%% first author
\author{Henry O. Jacobs, Owen K. Hughes, Matthew Johnson-Roberson, and Ram Vasudevan
\thanks{This work was supported by Ford Motor Company.}
 \thanks{ H.O. Jacobs, O. Hughes, and R.~Vasudevan are with the Department of Mechanical Engineering, University of Michigan, Ann Arbor, MI 48109
{\scriptsize \{\texttt{hojacobs,owhughes,ramv}\}~\texttt{@umich.edu}}}
\thanks{M. Johnson-Roberson is with the Department of Naval and Marine Engineering, University of Michigan, Ann Arbor, MI 48109\newline
{\scriptsize \texttt{mattjr@umich.edu}}}
}

@@

With a particular focus on the AV application several additional design criteria become important. 
First, false negative rates for unoccupied regions must be minimized.
The misclassification of space in this way has obvious safety issues.
Second, speed is paramount.
To effectively use human prediction within a vehicle control loop prediction rates must be commensurate with the speed at which humans change trajectories.
The margins between humans and vehicles are small and both frequently operate at the boundary. 
Finally, long-time horizon forecasting is preferable since this improves robot predictability, reduces operation close to safety margins, prevents the need for overly conservative or aggressive controllers and makes high-level goal planning more feasible.
This paper presents an algorithm for real-time, long-term prediction of pedestrian behavior which can subsequently be used by autonomous agents.
As depicted in Figure \ref{fig:gates-1-2}, this method works quickly to generate predictions that are precise while reducing the likelihood of false negative detections.

@@

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses.  In this figure, the dot is the start point of the test trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. In this example which was captured at thirty frames per second, the presented algorithm took 0.00465s per frame in a Python implementation. }
	\label{fig:gates-1-2}
\end{figure}

@@

\subsection{Background}
Most forecasting algorithm are well characterized by the underlying evolution model they adopt.
Such models come in a variety flavors, and are adapted to the task at hand (e.g. crowd modeling \cite{Helbing1992}).
This paper is focused on the construction of useful motion models for pedestrians that can aide the task of real-time forecasting for autonomous agents.
The simplest approach to forecasting with motion models forward integrates a Kalman filter \cite{kalman1960new} based upon the observed heading.
Over short time scales this method may perform well, but the resulting distribution devolves into an imprecise Gaussian mass over longer time scales.
This is a typical property of the extended Kalman filter and the Kalman filter with deterministic nonlinear drift \cite{Schneider2013}.
In particular, such models are less useful for forecasts beyond two seconds, especially when a pedestrian turns.
Nonetheless, these stochastic linear models serve as a reasonable default in the absence of any contextual knowledge.
For example, \cite{Kooji2014} uses a motion model of this variety, parametrized by latent variables, such as the pedestrian's awareness of nearby vehicles, to predict when and how a pedestrian may cross a street without leveraging any environmental context.

More sophisticated models that attempt to leverage environmental data include inverse optimal control (IOC) based models \cite{Ziebart2008,Ziebart2009,Kitani2012,Xie2013,Karasev2016}.
These IOC models have the desirable property of attributing intention and goal-seeking behavior to the agents.
For example, \cite{Kitani2012} extracts a Markov Decision Process (MDP) evolving on a finite 2D lattice by training on a small collection of features and trajectories.
The resulting MDP is light-weight since it is parametrized by only a small collection of coefficients equal in number to that of the feature maps.
Moreover, given an initial and final state, the probability distribution of the pedestrian at intermediate states is computable using matrix multiplication.
The speed of this computation, makes the algorithm of \cite{Kitani2012} a reasonable baseline for comparison for the algorithm that is presented in this paper.

The approach presented in \cite{Kitani2012} has been generalized in a variety of ways.
For example, time-dependent information, such as traffic signals, are incorporated in \cite{Karasev2016}, by relaxing the Markov property and considering a switched Markov process.
Other generalizations in \cite{Karasev2016} include replacing the finite-state space with a continuous one, and using a Markov jump process in the motion model.
Unfortunately the desired posteriors are difficult to compute in closed form, and as a result a sampling based method: a Rao-Blackwellized particle filter~\cite{Doucet2000} is employed.
The resulting accuracy of such methods can only be known in a probabilistic sense in that the error bounds are themselves random variables.
Moreover, accuracy can come at a large computational expensive which is prohibitive during real-time control.

One limitation of IOC models occurs in cases where there are many locally optimal solutions between a start and end goal.
In these cases, IOC type methods can yield non-robust and imprecise behavior.
This can occur, for example, when agents make sharp turns due to intermediate criteria on the way toward reaching their final destination.
To address this, \cite{Ballan2016} adopt an empiricists approach, computing ``turning maps'' and attempting to infer how agents behave in a given patch based on its feature and the behavior of previous agents on similar patches.
The motion model is a Markov jump process and the relevant posteriors were approximated using sample based techniques similar to \cite{Karasev2016}.
The objective of \cite{Ballan2016} is not only prediction, but the development of a motion model learned on one scene that could then subsequently be transferred to other scenes. 
This requires representations of ``objects'' in the scene that do not depend rigidly on the finitely many labels an engineer managed to think of in a late-night brainstorming session.
For example, such an algorithm should be able to infer how to behave near a roundabout by using prior knowledge of more fundamental building blocks like pavement, curbs, and asphalt.

Along similar lines to \cite{Ballan2016}, \cite{Walker2014} constructed an unsupervised approach towards forecasting.
As before, the motion model was a Markov jump process, and the training set was a collection unlabeled videos.
Unlike all the approaches mentioned thus far, the agents in \cite{Walker2014} were not manually specified.
They were learned by detecting which sort of patches of video were likely to move, and how.
The resulting predictions outperformed \cite{Kitani2012} when comparing the most likely path with the ground truth using the mean Hausdorff distance.
As in all methods mentioned thus far, computational speed and accuracy of any predicted posteriors were not a concern of \cite{Walker2014}, so no such results were reported.
However, since the motion model was a Markov jump process which required the application of a sample based technique, we should expect the same painful trade-off between error and speed to occur as in \cite{Karasev2016} and \cite{Ballan2016}.

\marginnote{\#1.1}
\rtext{On the other hand, many authors have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians. 
	Early work by \cite{Helbing1995} and \cite{Xu2012} describe pedestrians interactions using physically motivated methods. 
	Several models such as \cite{Yamaguchi2011}, \cite{Yi2016}, and \cite{Pellegrini2009} derive their motion models from \cite{Helbing1995} who incorporates collision avoidance through an interaction potential. 
	However this method suffers from not planning for other pedestrian' positions at future times. 
	\cite{Emonet2011}, \cite{Hospedales2009} , and \cite{Wang2009}  all take optical flow as input.
	\cite{Wang2009} and \cite{Emonet2011} both use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), where \cite{Hospedales2009} substitutes a Markov model. 
	These models are not agent based, and the lack of an explicit motion model limits their predictive power. 
	\cite{Koppula2016} predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances for humans and objects based on observed objectives within the scene. 
	\cite{Tay2008} , \cite{Wang2008}, and \cite{Trautman2015} create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories. 
	\cite{Alahi2016} uses Long Short-Term Memory (lstm) to learn pedestrian motion models without making assumptions about the manner in which agents will interact and is the state-of-the-art algorithm for socially based models while also having a quick run time.}

@@

The primary contributions of this paper are:
\begin{itemize}
	\item An accurate motion model for pedestrian forecasting.
	\item An expedient method for computing approximations of relevant posteriors generated by our motion model.
	\item Hard error bounds on the proposed approximations.
\end{itemize}
The method proposed by this paper is able to work three times faster than the existing state of the art while improving upon its performance over long time horizons.

For clarification, we should mention that there are a number of things that we do not do.
For example, we do not concern ourselves with detection and tracking. 
Nor do we concern ourselves with updating our prediction as new data comes along \cite{Kitani2012}.
We largely work in a 2D environment with a bird's eye view, operating under the assumption that the data has been appropriately transformed by a third party.
This is in contrast to \cite{Karasev2016}, which operates from first person video.
While it would be a straight forward extension to consider such things, it would detract from the presentation.
%Such questions are important, but beyond the scope of this paper, which concerns the underlying dynamic model.

The rest of the paper is organized as follows:
\begin{itemize}
	\item \S \ref{sec:model} describes our motion model as a Bayesian network.
	\item \S \ref{sec:efficient} describes how to compute probability densities for an agent's position efficiently.
	\item \S \ref{sec:implementation} demonstrates the model by training and testing it on the Stanford drone dataset \cite{Robicquet2016}.
\end{itemize}

@@

To numerically compute $\rho_t$, we build a probabilistic graphical model.
Our model assumes we have noisy information about agents, and each agent moves with some intention through the world in a way that is roughly approximated by a model.
Our model can be divided into three parts:
\begin{enumerate}
	\item Reality: This is parametrized by the true position for all time, $x_t$, and the initial velocity of the agent $v_0$.
	\item Measurements:  This is represented by our sensor readings $\hat{x}_0$ and $\hat{v}_0$ and are independent of all other variables given the true initial position and velocity, $x_o, v_0$.
	\item Motion Model: This is represented by a trajectory $\check{x}_t$ and depends on a variety of other variables which are described below.
\end{enumerate}
We now elaborate on these three components, and relate them to one another.
Many of the choices we make are motivated by a balance between model quality and computational speed (see \S \ref{sec:efficient}).

@@

If the agent is of nonlinear type, then we assume the dynamics take the form:
\begin{align}n
	\frac{d \check{x}_t}{dt} = s \cdot X_k(\check{x}_t) \label{eq:ode}
\end{align}
where $X_k$ is a vector-field\footnote{A vector-field, generally speaking, is an assignment of a velocity to each position in some space.  A vector-field on $\mathbb{R}^n$ is nothing but a map from $\mathbb{R}^n \to \mathbb{R}^n$.} drawn from a finite collection $\{X_1, \dots, X_n\}$, and $s \in \mathbb{R}$.
More specifically, we assume that each $X_k$ has the property that $\| X_k(x) \| = 1$ for all $x \in D$.
This property ensures that speed is constant in time.
% and it has the further advantage of being the (local) generator of solutions to an optimal navigation problem (see Appendix \ref{app:ioc}).
As we describe in \S \ref{sec:implementation}, the stationary vector-fields $X_1,\dots,X_n$ are learned from the dataset.

>>>>

%  For math environment 
\usepackage{amsmath,amssymb}
%\usepackage[linesnumbered]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{marginnote}
%\usepackage{algorithm2e}
\usepackage{caption}
%  For todo notes
\usepackage{todonotes}
%  For drawing Bayesian networks
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{tikz-cd}
\usepackage[justification=justified,font=footnotesize]{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{array}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{comment}
\usepackage{color}  % For Highlighting
%\usepackage{natbib}
\usepackage[noadjust]{cite}

@@

%%% first author
\author{Henry O. Jacobs, Owen K. Hughes, Matthew Johnson-Roberson, and Ram Vasudevan
 \thanks{ H.O. Jacobs, O. Hughes, M. Johnson-Roberson, and R.~Vasudevan are with the University of Michigan, Ann Arbor, MI 48109
{\scriptsize \{\texttt{hojacobs,owhughes,mattjr,ramv}\}~\texttt{@umich.edu}}}
\thanks{This work was supported by Ford Motor Company.}
}

@@

With a particular focus on the AV application several additional design criteria become important. 
First, false negative rates for unoccupied regions must be minimized.
The misclassification of space in this way has obvious safety issues.
Second, speed is paramount.
To effectively use human prediction within a vehicle control loop prediction rates must be commensurate with the speed at which humans change trajectories.
%The margins between humans and vehicles are small and both frequently operate at the boundary. 
Finally, long-time horizon forecasting is preferable since this improves robot predictability, reduces operation close to safety margins, prevents the need for overly conservative or aggressive controllers and makes high-level goal planning more feasible.
This paper presents an algorithm for real-time, long-term prediction of pedestrian behavior which can subsequently be used by autonomous agents.
As depicted in Figure \ref{fig:gates-1-2}, this method works quickly to generate predictions that are precise while reducing the likelihood of false negative detections.

@@

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses. The dot is the starting point of the trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. The presented algorithm took $0.00465$s per frame in a Python implementation. }
	\label{fig:gates-1-2}
	\vspace*{-0.7cm}
\end{figure}

@@

\subsection{Background}
Most forecasting algorithm are well characterized by the underlying evolution model they adopt.
Such models come in a variety flavors, and are adapted to the task at hand (e.g. crowd modeling \cite{Helbing1992}).
This paper is focused on the construction of useful motion models for pedestrians that can aide the task of real-time forecasting for autonomous agents.
The simplest approach to forecasting with motion models forward integrates a Kalman filter based upon the observed heading.
Over short time scales this method may perform well, but the resulting distribution devolves into an imprecise Gaussian mass over longer time scales.
%This is a typical property of the extended Kalman filter and the Kalman filter with deterministic nonlinear drift \cite{Schneider2013}.
In particular, such models are less useful for forecasts beyond two seconds, especially when a pedestrian turns.
Nonetheless, these stochastic linear models serve as a reasonable default in the absence of any contextual knowledge.
%For example, \cite{Kooji2014} uses a motion model of this variety, parametrized by latent variables, such as the pedestrian's awareness of nearby vehicles, to predict when and how a pedestrian may cross a street without leveraging any environmental context.

More sophisticated models that attempt to leverage environmental data include Inverse Optimal Control (IOC) based models \cite{Ziebart2008,Ziebart2009,Kitani2012,Xie2013,Karasev2016}.
These IOC models have the desirable property of attributing intention and goal-seeking behavior to the agents.
For example, \cite{Kitani2012} extracts a Markov Decision Process (MDP) evolving on a finite 2D lattice by training on a small collection of features and trajectories.
The resulting MDP is light-weight since it is parametrized by only a small collection of coefficients equal in number to that of the feature maps.
Moreover, given an initial and final state, the probability distribution of the pedestrian at intermediate states is computable using matrix multiplication.
The speed of this computation, makes the algorithm of \cite{Kitani2012} a reasonable baseline for comparison for the algorithm that is presented in this paper.

%The approach presented in \cite{Kitani2012} has been generalized in a variety of ways.
This approach has been generalized in a variety of ways.
For example, time-dependent information, such as traffic signals, are incorporated in \cite{Karasev2016}, by relaxing the Markov property and considering a switched Markov process.
Other generalizations include replacing the finite-state space with a continuous one, and using a Markov jump process in the motion model.
Unfortunately the desired posteriors are difficult to compute in closed form, and as a result a sampling based method.
The resulting accuracy of such methods, which can come at a large computational expense, can only be known in a probabilistic sense in that the error bounds are themselves random variables.
%Moreover, accuracy can come at a large computational expense.
% which is prohibitive during real-time control.

One limitation of IOC models occurs in cases where there are locally optimal solutions between a start and end goals which can yield non-robust and imprecise behavior.
This can occur when agents make sharp turns due to intermediate criteria on the way toward reaching their final destination.
To address this, \cite{Ballan2016} adopt an empiricists approach, computing ``turning maps'' and attempting to infer how agents behave in a given patch.
The motion model is a Markov jump process and the relevant posteriors are approximated using sample based techniques similar to \cite{Karasev2016}.
The objective of \cite{Ballan2016} is not only prediction, but the development of a motion model learned on one scene that could then subsequently be transferred to other scenes. 
This requires representations of ``objects'' in the scene that do not depend rigidly on the finitely many labels an engineer managed to think of in a late-night brainstorming session.
%For example, such an algorithm should be able to infer how to behave near a roundabout by using prior knowledge of more fundamental building blocks like pavement, curbs, and asphalt.

Recent work has focused on constructing an unsupervised approach towards forecasting  \cite{Walker2014}.
%As before, the motion model was a Markov jump process, and the training set was a collection unlabeled videos.
Unlike all the approaches mentioned thus far, the agents in \cite{Walker2014} were not manually specified.
They were learned by detecting which sort of patches of video were likely to move, and how.
The resulting predictions outperformed \cite{Kitani2012} when comparing the most likely path with the ground truth using the Modified Hausdorff Distance.
As in all methods mentioned thus far, computational speed and accuracy of any predicted posteriors were not a concern, so no such results were reported.
However, since the motion model was a Markov jump process which required the application of a sample based technique, we should expect the same painful trade-off between error and speed to occur as in \cite{Karasev2016,Ballan2016}.

\reversemarginpar
\marginnote{\#1.1}
\rtext{Many have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians using physically motivated methods \cite{Helbing1995,Xu2012}. 
	Several models derive their motion models from \cite{Helbing1995} by incorporating collision avoidance through an interaction potential \cite{Pellegrini2009,Yamaguchi2011,Yi2016}. 
	However this method suffers from not planning for other pedestrian positions at future times. 
	Others take optical flow as input \cite{Hospedales2009,Wang2009,Emonet2011}.
	These approaches use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), or on a Markov model. 
	 These models are not agent based, and the lack of an explicit motion model limits their predictive power. 
	 Recently methods have been developed to predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate learned affordances based on observed objectives within the scene \cite{Koppula2016}. 
	 Others create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories \cite{Tay2008,Wang2008,Trautman2015}. 
	Most recently a method using Long Short-Term Memory (lstm) to learn pedestrian motion models without making assumptions about the manner in which agents interact is the state-of-the-art algorithm for socially based models and has a rapid computation time \cite{Alahi2016}.}

@@

The primary contributions of this paper are three-fold: first, an accurate motion model for pedestrian forecasting, second, an expedient method for computing approximations of relevant posteriors generated by our motion model, and finally hard error bounds on the proposed approximations.
The method proposed by this paper is able to work three times faster than the existing state of the art while improving upon its performance over long time horizons.
For clarification, we should mention that there are a number of things that we do not do.
For example, we do not concern ourselves with detection and tracking. 
Nor do we concern ourselves with updating our prediction as new data comes along.
We largely work in a 2D environment with a bird's eye view, operating under the assumption that the data has been appropriately transformed by a third party.
%This is in contrast to \cite{Karasev2016}, which operates from first person video.
While it would be a straight forward extension to consider a first person perspective, it would detract from the presentation.
%Such questions are important, but beyond the scope of this paper, which concerns the underlying dynamic model.

The rest of the paper is organized as follows: \S \ref{sec:model} describes our motion model as a Bayesian network, \S \ref{sec:efficient} describes how to compute probability densities for an agent's position efficiently, and \S \ref{sec:implementation} demonstrates the model by training and testing it on the Stanford drone dataset \cite{Robicquet2016}.

@@

To compute $\rho_t$, we build a probabilistic graphical model, which is composed of three parts:
%Our model assumes we have noisy information about agents, and each agent moves with some intention through the world.
%Our model is divided into three parts:
\begin{enumerate}
	\item Reality: This is parametrized by the true position for all time, $x_t$, and the initial velocity of the agent $v_0$.
	\item Measurements:  This is represented by our sensor readings $\hat{x}_0$ and $\hat{v}_0$ and are independent of all other variables given the true initial position and velocity, $x_o, v_0$.
	\item Motion Model: This is represented by a trajectory $\check{x}_t$ and depends on a variety of other variables.
\end{enumerate}
We elaborate on these three components next.
%Many of the choices are motivated by a balance between model quality and computational speed.

@@

If the agent is of nonlinear type, then we assume the dynamics take the form:
\begin{align}n
	\frac{d \check{x}_t}{dt} = s \cdot X_k(\check{x}_t) \label{eq:ode}
\end{align}
where $X_k$ is a vector-field\footnote{A vector-field is an assignment of a velocity to each position in some space.  A vector-field on $\mathbb{R}^n$ is a map from $\mathbb{R}^n \to \mathbb{R}^n$.} drawn from a finite collection $\{X_1, \dots, X_n\}$, and $s \in \mathbb{R}$.
More specifically, we assume that each $X_k$ has the property that $\| X_k(x) \| = 1$ for all $x \in D$.
This property ensures that speed is constant in time.
% and it has the further advantage of being the (local) generator of solutions to an optimal navigation problem (see Appendix \ref{app:ioc}).
As we describe in \S \ref{sec:implementation}, the stationary vector-fields $X_1,\dots,X_n$ are learned from the dataset.
